\documentclass[a4paper,12pt,oneside,pdflatex,italian,final,twocolumn]{article}

\usepackage[utf8]{inputenc}
\usepackage{parallel}
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage{fancyhdr}

\usepackage[export]{adjustbox}
\usepackage[margin=0.5in]{geometry}
\addtolength{\topmargin}{0in}

\usepackage{libertine}
\renewcommand*\familydefault{\sfdefault}  %% Only if the base font of the document is to be sans serif
\usepackage[T1]{fontenc}

\title{ MCP9808 }
\author{ Joe Smith }
\date{ 2019 }

\begin{document}

\pagestyle{fancy}

\lhead{ Joe Smith }
\chead { 2019 }
\rhead{ MCP9808 v0.1.0 }


\onecolumn


\begin{figure}
\begin{minipage}{0.47\textwidth}

\section{Overview}
    This is a test description
    \begin{itemize}
        \item Device addresses:
          24,
          25,
          26,
          27,
          28,
          29,
          30,
          31
        \item Address type 7-bit
    \end{itemize}


\end{minipage}
\hfill

\end{figure}


\section{Register Description}
\begin{itemize}
\item Configuration Register - The MCP9808 has a 16-bit Configuration register (CONFIG) that
allows the user to set various functions for a robust temperature
monitoring system.
Bits 10 through 0 are used to select the temperature alert output
hysteresis, device shutdown or Low-Power mode, temperature boundary
and critical temperature lock, and temperature Alert output
enable/disable.
In addition, Alert output condition (output set for TUPPER and
TLOWER temperature boundary or TCRIT only), Alert output status
and Alert output polarity and mode (Comparator Output or Interrupt
Output mode) are user-configurable.

\end{itemize}

\section{Technical specification}
\centering
\begin{tabular}{lcrr}
\toprule
 & Register Name & Register Address & Register Length \\
\midrule
configuration & Configuration Register & 1 & 16 \\
\bottomrule
\end{tabular}

\raggedright

\section{Fields}



\raggedright

\subsection{Register configuration}
\centering
\begin{tabular}{lcr}
\toprule
  & Field Name & Bits \\
\midrule
limitHysteresis & TUPPER and TLOWER Limit Hysteresis bits &
10:9
\\
shutdownMode & Shutdown Mode bit &
8
\\
\bottomrule

\end{tabular}


\raggedright

\subsubsection{Field limitHysteresis }

This bit can not be altered when either of the Lock bits are set
(bit 6 and bit 7). This bit can be programmed in Shutdown mode.


\begin{itemize}
\item Temp\_0C (0) - 0°C (power-up default)
\item Temp\_1C5 (1) - +1.5°C
\item Temp\_3C (2) - +3.0°C
\item Temp\_6C (3) - +6.0°C
\end{itemize}


\raggedright

\subsubsection{Field shutdownMode }

In shutdown, all power-consuming activities are disabled, though
all registers can be written to or read. This bit cannot be set
to ‘1’ when either of the Lock bits is set (bit 6 and bit 7).
However, it can be cleared to ‘0’ for continuous conversion while
locked.


\begin{itemize}
\item continousConversion (0) - Continuous conversion (power-up default)
\item shutdown (1) - Shutdown (Low-Power mode)
\end{itemize}





\end{document}